---
title: "Supplemenetary materials for Quantifying and Reducing Speaker Heterogeneity within the Common Voice Corpus for Phonetic Analysis (Interspeech 2025)"
author: "Miao Zhang, Aref Farhadipour, Annie Baker, Jiachen Ma, Bogdan Pricop, Eleanor Chodroff"
date: "2025-05-30"
format: html
---



```{r load packages}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
# Set up the packages and functions needed to perform the analysis.
# List of required packages
required_packages <- c(
  "tidyverse",
  "ggdist",
  "ggview",
  "irr",
  "lme4",
  "ggeffects"
)

# Install any packages that are not already installed
installed_packages <- rownames(installed.packages())
packages_to_install <- setdiff(required_packages, installed_packages)

if (length(packages_to_install) > 0) {
  install.packages(packages_to_install)
}

# Load all required packages
invisible(lapply(required_packages, library, character.only = TRUE))

# Set the plotting theme
theme_set(theme_ggdist())

# The function to create score bins
create_scoreBin <- function(df) {
  df <- df |> 
    mutate(
      score_bin = case_when(
        score < 0.1 ~ "\u003c 0.1",
        score < 0.2 ~ "\u003c 0.2",
        score < 0.3 ~ "\u003c 0.3",
        score < 0.4 ~ "\u003c 0.4",
        score < 0.5 ~ "\u003c 0.5",
        .default = "\u003c 1.0"),
      score_bin = factor(score_bin, levels = c("\u003c 0.1", 
                                               "\u003c 0.2", 
                                               "\u003c 0.3", 
                                               "\u003c 0.4", 
                                               "\u003c 0.5", 
                                               "\u003c 1.0")))
  return(df)
}
```

## Similarity scores

Download the similarity score file from [VoxCommunis](https://huggingface.co/datasets/pacscilab/VoxCommunis/blob/main/similarity_scores.txt).

```{r get the similarity scores}
col_names <- c("test", "enroll", "score")
# Replace the file path with the one on your computer
scores <- read_delim("/Users/miaozhang/Documents/GitHub/CV_clientID_cleaning/similarity_scores.txt", col_names = col_names, show_col_types = FALSE)
threshold = 0.38288
scores <- scores |> mutate(lang_code = str_extract(enroll, "(?<=voice_)[^_]+"), # Get the languages
                           under_threshold = if_else(score < threshold, T, F))
glimpse(scores)
```

Plot the distribution of the similarity scores across all languages.

```{r histogram of scores}
scores |> 
  ggplot(aes(score)) +
  geom_histogram(aes(fill = after_stat(density)), bins = 40,
                 show.legend = F) +
  #geom_vline(xintercept = 0.38, color = "red3", linewidth = 0.5) +
  scale_fill_viridis_c() +
  scale_y_continuous(expand = expansion(mult = c(0, .1)),
                     label = scales::label_number(scale = 1/100000)) +
  scale_x_continuous(breaks = c(0, 0.4, 0.8)) +
  labs(y = expression("Count (\u00D710,000)"), x = "Similarity score") +
  coord_cartesian(xlim = c(-0.1, 1.0)) +
  theme(panel.grid.major.x = element_line(linewidth = 0.4),
        panel.grid.minor.x = element_line(linewidth = 0.2),
        panel.grid.major.y = element_line(linewidth = 0.4),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14),
        axis.title.x = element_text(size=16),
        axis.title.y = element_text(size=13)) 

```


The next step require downloading speaker files from [VoxCommunis Corpus](https://huggingface.co/datasets/pacscilab/VoxCommunis).

```{r get speaker files}
# Replace the path below with the one on your own computer
spkr_dir <- "/Users/miaozhang/Research/VoxCommunis/VoxCommunis_Huggingface/speaker_files"
spkr_files <- list.files(spkr_dir, pattern = "*.tsv", full.names = T)

spkr_files <- map_dfr(spkr_files, \(x) read_tsv(x, col_select = c("path", "speaker_id"), show_col_types = FALSE))
spkr_files <- mutate(spkr_files, speaker_id = paste(str_extract(path, "(?<=voice_)[^_]+"), speaker_id, sep = "_"))
spkr_files <- rename(spkr_files, test = path)

spkr_files <- mutate(spkr_files, test = str_replace(test, ".mp3", ""))
scores <- mutate(scores, test = str_replace(test, ".wav", ""))

scores <- inner_join(scores, spkr_files, by = "test")
glimpse(scores)

prop_under_threshold_by_lang <- scores |> 
  summarize(prop_threshold = sum(under_threshold)/n(), .by = lang_code)
```

Evaluate how much the client IDs are affected by the heterogeneous speaker issue by looking into how many client IDs that contain recordings from multiple speakers there are.

```{r get data ready for evaluating speaker heterogeneity}
speaker_id_impact <- scores |> 
  summarize(n = n(), prop_threshold = sum(under_threshold)/n(), .by = speaker_id) |> 
  mutate(affected = if_else(prop_threshold > 0, T, F),
         more_than_10 = if_else(prop_threshold > 0.10, T, F),
         lang = str_extract(speaker_id, "^[^_]+")) 
n_affected_more_than_10 <- speaker_id_impact |> 
  summarize(n_affected = sum(more_than_10),
            n_total = n(), 
            perc = n_affected/n_total,
            .by = lang) 

prop_more_than_100 <- scores |> summarize(n = n() + 1, .by = c(lang_code, speaker_id)) |> 
  mutate(more_than_100 = if_else(n >= 100, T, F)) |> 
  summarize(prop_more_than_100 = sum(more_than_100)/n(),
            n = n(),
            .by = lang_code)


```

Plot the the degree to which client IDs and languages are affected.

```{r plot the heterogeneity results}
# The proportion of files in each language with a score under the threshold
prop_under_threshold_by_lang |> 
  ggplot(aes(reorder(lang_code, -prop_threshold), prop_threshold, fill = prop_threshold)) +
  geom_col() +
  scale_fill_viridis_c() +
  scale_y_continuous(labels = scales::percent_format(), lim = c(0,0.3), 
                     expand = expansion(mult = c(0, .01))) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.35, size = 11),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major.y = element_line(linetype = 3),
        legend.title = element_blank())

# The proportion of client IDs that have more than 10% of the associated recordings with a score lower than the threshold
ggplot(n_affected_more_than_10, aes(reorder(lang, desc(perc)), perc, fill = perc)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_percent(), expand = expansion(mult = c(0, 0.1))) +
  scale_fill_viridis_c() +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 11),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.title = element_blank(),
        panel.grid.major.y = element_line(linetype = 3))

```


## Auditing result: round 1



Read in the auditing result from round 1.

```{r get audit r1 data}
audit_r1 <- read_csv("/Users/miaozhang/Documents/GitHub/CV_clientID_cleaning/audit_r1.csv") |> 
  create_scoreBin() |> 
  mutate(validation = factor(validation, 
                             levels = c("Different Speaker", "Audio Quality Issue", 
                                        "Missing Speech", "Not Sure", "Same Speaker")))
glimpse(audit_r1)
```

Plot the round 1 results.

```{r r1 results plotting}
ggplot(audit_r1, aes(x = score_bin, fill = validation)) + 
  stat_count(position = "dodge") +
  scale_fill_viridis_d(end = 0.98, begin = 0.05, alpha = 0.9) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  theme_ggdist(base_size = 6.5) +
  theme(axis.title.x = element_blank(),
        panel.grid.major.y = element_line(linetype = 3, linewidth = 0.8),
        axis.text = element_text(size = 16),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 13),
        legend.position = "bottom",
        legend.title = element_blank()) 
```

## Auditing result: round 1

Get the round 2 data.

```{r get audit r2 data}
audit_r2 <- read_csv("/Users/miaozhang/Documents/GitHub/CV_clientID_cleaning/audit_r2.csv") |> create_scoreBin()
glimpse(audit_r2)
```

Calculate the Fleiss' Kappa.

```{r fleiss kappa}
kappa_dat <- audit_r2[, colnames(audit_r2) %in% c("validation1", "validation2", "validation3", "validation4", "validation5")]
kappam.fleiss(kappa_dat)
```

Fit a GLMER model to evaluate the threshold to reject same speaker hypothesis.

```{r make the data into long format}
audit_r2_long <- audit_r2 %>% pivot_longer(cols = starts_with("person"), 
                             names_to = ("person"), 
                             values_to = "name") %>% 
  pivot_longer(cols = starts_with("validation"), 
               names_to = ("validation"), 
               values_to = "val")
audit_r2_long <- subset(audit_r2_long, name == "Annotator1" & validation == "validation1" |
                   name == "Annotator2" & validation == "validation2" |
                   name == "Annotator3" & validation == "validation3" |
                   name == "Annotator4" & validation == "validation4" |
                   name == "Annotator5" & validation == "validation5")
glimpse(audit_r2_long)
```

```{r fit the glmer model}
samediff_all <- subset(audit_r2_long, val %in% c("Same Speaker","Different Speaker"))
samediff_all$nVal <- ifelse(samediff_all$val == "Same Speaker", 1, 0)
mod <- glmer(nVal ~ score + (1 | person) + (0 + score | person), family = "binomial", data = samediff_all)
```

Get the threshold.

```{r obtain the threshold}
threshold <- -fixef(mod)[1]/fixef(mod)[2]
threshold
```

Plot the model result.

```{r plot the threshold}
samediff_all$predicted <- predict(mod, type = "response", re.form = NA)
samediff_all$predicted_person <- predict(mod, type = "response")
preds <- ggpredict(mod, terms = "score[all]", interval = "confidence")

ggplot(samediff_all, aes(x = score, y = nVal)) +
  geom_jitter(alpha = 0.08, width = 0.05, height = 0.05) +
  # Confidence interval ribbon
  geom_ribbon(data = preds, aes(x = x, ymin = conf.low, ymax = conf.high), 
              fill = "deepskyblue3", alpha = 0.2, inherit.aes = FALSE) +
  # Model prediction line
  geom_line(data = preds, aes(x = x, y = predicted), 
            color = "deepskyblue3", size = 1.2, inherit.aes = FALSE) +
  scale_x_continuous(limits = c(-0.2, 1)) +
  labs(x = "Similarity Score", y = "Probability") +
  geom_vline(xintercept = threshold, linetype = "dashed", color = "red") +
  theme_minimal() +
  theme(panel.grid.minor = element_blank()) 
```


