---
title: "Supplementary materials for Quantifying and Reducing Speaker Heterogeneity within the Common Voice Corpus for Phonetic Analysis (Interspeech 2025)"
author:
  - name: Miao Zhang
  - name: Aref Farhadipour
  - name: Annie Baker
  - name: Jiachen Ma
  - name: Bogdan Pricop
  - name: Eleanor Chodroff
format: html
---

## Introduction

This .qmd file is intended to reproduce the results and visualizations from the paper [Zhang, M., Farhadipour, A., Baker, A., Ma, J., Pricop, B., Chodroff, E. (2025) Quantifying and Reducing Speaker Heterogeneity within the Common Voice Corpus for Phonetic Analysis. Proc. Interspeech 2025, 3933-3937, doi: 10.21437/Interspeech.2025-2027](https://www.isca-archive.org/interspeech_2025/zhang25s_interspeech.pdf).

This paper addresses the problem of speaker heterogeneity in the Mozilla Common Voice corpus, where a single “client ID” may include recordings from multiple speakers, complicating phonetic analysis and speech technology development. We use ResNet-293-based speaker embeddings to compute similarity scores between utterances within the same client ID and then design a speaker discrimination task to determine an optimal similarity threshold. Through large-scale evaluation across 76 languages, we identify a threshold of 0.354 that effectively reduces speaker heterogeneity while minimizing data loss (averaging 3.5% per language). 

### How to use this script

There are several data files you need to download from the repo to run this script yourself.

1. [The similarity scores](https://huggingface.co/datasets/pacscilab/VoxCommunis/blob/main/similarity_scores_interspeech2025.txt)
2. [The speaker files](https://huggingface.co/datasets/pacscilab/VoxCommunis/tree/main/speaker_files)
3. [First round audit results](https://github.com/pacscilab/CV_clientID_cleaning/blob/main/audit_r1.csv)
4. [Second round audit results](https://github.com/pacscilab/CV_clientID_cleaning/blob/main/audit_r2.csv)

```{r load packages}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
# Set up the packages and functions needed to perform the analysis.
# List of required packages
required_packages <- c(
  "tidyverse",
  "ggdist",
  "ggview",
  "irr",
  "lme4",
  "ggeffects"
)

# Install any packages that are not already installed
installed_packages <- rownames(installed.packages())
packages_to_install <- setdiff(required_packages, installed_packages)

if (length(packages_to_install) > 0) {
  install.packages(packages_to_install)
}

# Load all required packages
invisible(lapply(required_packages, library, character.only = TRUE))

# Set the plotting theme
theme_set(theme_ggdist())

# The function to create score bins
create_scoreBin <- function(df) {
  df <- df |> 
    mutate(
      score_bin = case_when(
        score < 0.1 ~ "\u003c 0.1",
        score < 0.2 ~ "\u003c 0.2",
        score < 0.3 ~ "\u003c 0.3",
        score < 0.4 ~ "\u003c 0.4",
        score < 0.5 ~ "\u003c 0.5",
        .default = "\u003c 1.0"),
      score_bin = factor(score_bin, levels = c("\u003c 0.1", 
                                               "\u003c 0.2", 
                                               "\u003c 0.3", 
                                               "\u003c 0.4", 
                                               "\u003c 0.5", 
                                               "\u003c 1.0")))
  return(df)
}
```

## Similarity scores

Load the similarity score file into R and obtain some descriptive stats.

```{r get the similarity scores}
# Define the column names of the similarity score file.
col_names <- c("test", "enroll", "score")

# Replace the file path with the one on your computer
path2scores <- "/Users/miaozhang/Research/VoxCommunis/VoxCommunis_Huggingface/similarity_scores_interspeech2025.txt"
scores <- read_delim(path2scores, col_names = col_names, show_col_types = FALSE, delim = " ")

# Use the threshold from our paper
threshold = 0.354

# Get the language codes and check if the file has a score under the threshold
scores <- scores |> mutate(lang_code = str_extract(enroll, "(?<=voice_)[^_]+"), # Get the languages
                           under_threshold = if_else(score < threshold, T, F))
glimpse(scores)

# Get some summary of the similarity scores
summary(scores$score)
scores_by_lang <- scores |>
  group_by(lang_code) |> 
  summarise(q1 = quantile(score, 0.25), 
            median = median(score), 
            q3 = quantile(score, 0.75))
summary(scores_by_lang$q1)
summary(scores_by_lang$q3)
```

Plot the distribution of the similarity scores.

```{r histogram of scores}
# Adjust the figure plotting setting
#| fig-width: 6
#| fig-height: 3.5
#| fig-align: center

scores |> 
  ggplot(aes(score)) +
  geom_histogram(aes(fill = after_stat(density)), bins = 40,
                 show.legend = F) +
  scale_fill_viridis_c() +
  scale_y_continuous(expand = expansion(mult = c(0, .1)),
                     label = scales::label_number(scale = 1)) +
  scale_x_continuous(breaks = c(0, 0.4, 0.8)) +
  labs(y = expression("Count"), x = "Similarity score") +
  coord_cartesian(xlim = c(-0.1, 1.0)) +
  theme(panel.grid.major.x = element_line(linewidth = 0.4),
        panel.grid.minor.x = element_line(linewidth = 0.2),
        panel.grid.major.y = element_line(linewidth = 0.4),
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        axis.title.x = element_text(size=16),
        axis.title.y = element_text(size=16)) 
```
Then load the speaker files.

```{r get speaker files}
# Replace the path below with the one on your own computer
spkr_dir <- "/Users/miaozhang/Research/VoxCommunis/VoxCommunis_Huggingface/speaker_files"
spkr_files <- list.files(spkr_dir, pattern = "*.tsv", full.names = T)

spkr_files <- map_dfr(spkr_files, \(x) read_tsv(x, col_select = c("path", "speaker_id"), show_col_types = FALSE))

# Unify the extension in both datasets
spkr_files <- mutate(spkr_files, 
                     speaker_id = paste(str_extract(path, "(?<=voice_)[^_]+"), speaker_id, sep = "_")) |>
  rename(test = path) |> 
  mutate(test = str_replace(test, ".mp3", ""))
scores <- mutate(scores, test = str_replace(test, ".wav", ""))

# join the two datasets together
scores <- inner_join(scores, spkr_files, by = "test")
glimpse(scores)

# Get the propotion of files under the threshold in each language
prop_under_threshold_by_lang <- scores |> 
  summarize(prop_threshold = sum(under_threshold)/n(), .by = lang_code)
```

Evaluate to what extent the client IDs are affected by speaker heterogeneity by looking into the number of client IDs that contain recordings from multiple speakers.

```{r get data ready for evaluating speaker heterogeneity}
# Summarize by speaker_id: compute number of files (n) and proportion under threshold
speaker_id_impact <- scores |> 
  summarize(
    n = n() + 1,  
    prop_threshold = sum(under_threshold) / (n() + 1),  
    .by = speaker_id
  ) |> 
  mutate(
    affected = if_else(prop_threshold > 0, T, F),          # Check if any of the recordings under the client ID are from a different speaker
    more_than_10 = if_else(prop_threshold > 0.10, T, F),  # Check if more than 10% of the recordings under the client ID are from a different speaker
    lang = str_extract(speaker_id, "^[^_]+")              
  )

# Count how many speakers are affected by >10% under threshold, per language
n_affected_more_than_10 <- speaker_id_impact |> 
  summarize(
    n_affected = sum(more_than_10),         # number of speakers with >10% affected
    n_total = n(),                          # total speakers
    perc = n_affected / n_total,            # proportion affected
    .by = lang
  )

# For each speaker, count if they have more than 100 files
prop_more_than_100 <- scores |> 
  summarize(n = n() + 1, .by = c(lang_code, speaker_id)) |> 
  mutate(more_than_100 = if_else(n >= 100, T, F)) |>   # flag speakers with >= 100 files
  summarize(
    prop_more_than_100 = sum(more_than_100) / n(),     # proportion of speakers with >= 100 files
    n = n(),                                          # total speakers
    .by = lang_code
  )

# Check the distribution of prop_threshold by language
print("Proportion of files under the threshold by language:")
print(summary(prop_under_threshold_by_lang$prop_threshold))

# Count speakers under various cutoff conditions
print(paste("Languages with <10% under threshold:", 
            nrow(subset(prop_under_threshold_by_lang, prop_threshold < 0.1))))

print(paste("Number of Client IDs with <10% under threshold: ", 
            nrow(subset(speaker_id_impact, prop_threshold < 0.1))))

print(paste("Proportion of client IDs <10% under threshold:", 
            round(nrow(subset(speaker_id_impact, prop_threshold < 0.1)) / 
                    nrow(speaker_id_impact), 3)))  

# Summarize affected speakers by language and whether >10% affected
affected_ids <- speaker_id_impact |>
  group_by(lang, more_than_10) |>
  summarise(greaterThan10 = n()) |>          # count speakers per lang × condition
  pivot_wider(names_from = more_than_10, values_from = greaterThan10) |> 
  rename("good" = `FALSE`,                   # "good" = speakers not badly affected
         "bad" = `TRUE`) |>                  # "bad" = speakers with >10% data affected
  mutate(
    bad = ifelse(is.na(bad), 0, bad),        # replace NA with 0 for langs with no "bad" speakers
    total = sum(good + bad),                 # total speakers per language
    prop = bad / total                       # proportion of "bad" speakers
  )

# Distribution of bad-speaker proportions across languages
print("The proportion of client IDs that contain different speaker's voices in more than 10% of the associated recordings")
summary(affected_ids$prop)
```

Plot the the degree to which client IDs and languages are affected.

```{r plot the heterogeneity results}
# Adjust the figure plotting setting
#| fig-width: 6
#| fig-height: 3.5
#| fig-align: center

# The proportion of files in each language with a score under the threshold
prop_under_threshold_by_lang |> 
  ggplot(aes(reorder(lang_code, -prop_threshold), prop_threshold, fill = prop_threshold)) +
  geom_col() +
  scale_fill_viridis_c() +
  scale_y_continuous(lim = c(0,0.25), 
                     expand = expansion(mult = c(0, .01))) +
  guides(fill = "none") +
  #ylab("Prop. utterances") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.35, size = 8),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        #axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.ticks.x = element_blank(),
        panel.grid.major.y = element_line(linetype = 3),
        legend.title = element_blank())
#ggsave("~/Desktop/dist_scores.pdf", plot=last_plot(), dpi = 300, height = 3, width = 7)

# The proportion of client IDs that have more than 10% of the associated recordings with a score lower than the threshold
ggplot(n_affected_more_than_10, aes(reorder(lang, desc(perc)), perc, fill = perc)) +
  geom_col() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  scale_fill_viridis_c() +
  guides(fill = "none") +
  #ylab("Prop. client IDs") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.35, size = 8),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        #axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.ticks.x = element_blank(),
        legend.title = element_blank(),
        panel.grid.major.y = element_line(linetype = 3))
#ggsave("~/Desktop/under_threshold_perc.pdf", plot=last_plot(), dpi = 300, height = 3, width = 7)
```


## Auditing result: round 1

Read in the auditing result from round 1.

```{r get audit r1 data}
# load the first round audit result
audit_r1 <- read_csv("~/Documents/GitHub/miaozhang/static/papers_slides/audit_r1.csv") |> 
  create_scoreBin() |> 
  mutate(validation = factor(validation, 
                             levels = c("Different Speaker", 
                                        "Same Speaker",
                                        "Audio Quality Issue", 
                                        "Missing Speech", 
                                        "Not Sure"
                                        )))
glimpse(audit_r1)
```

Plot the round 1 results.

```{r r1 results plotting}
# Adjust the figure plotting setting
#| fig-width: 6
#| fig-height: 3.5
#| fig-align: center


ggplot(audit_r1, aes(x = score_bin, fill = validation)) + 
  stat_count(position = "dodge") +
  scale_fill_manual(values = c("#5a2b75", "#3d9e96", "#f3e740", "#4a6b99", "#6bcd72")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  #theme_ggdist(base_size = 6.5) +
  ylab("Count") + 
  guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
  theme(axis.title.x = element_blank(),
        panel.grid.major.y = element_line(linetype = 3, linewidth = 0.8),
        axis.text = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.text = element_text(size = 15),
        legend.position = "bottom",
        legend.title = element_blank()) 
#ggsave("~/Desktop/vxc-spkr-val.pdf", plot=last_plot(), dpi = 300, height = 3, width = 7)
```

## Auditing result: round 1

Get the round 2 data.

```{r get audit r2 data}
audit_r2 <- read_csv("~/Documents/GitHub/miaozhang/static/papers_slides/audit_r2.csv") |> create_scoreBin()
glimpse(audit_r2)
```

Calculate the Fleiss' Kappa.

```{r fleiss kappa}
kappa_dat <- audit_r2[, colnames(audit_r2) %in% c("validation1", "validation2", "validation3", "validation4", "validation5")]
kappa_result <- kappam.fleiss(kappa_dat)
print(paste0("The Fleiss' Kappa = ", round(kappa_result$value, 2)))
```

Fit a GLMM model to evaluate a threshold for rejecting same-speaker hypothesis.

```{r make the data into long format}
audit_r2_long <- audit_r2 |> 
  pivot_longer(cols = starts_with("person"), names_to = ("person"), values_to = "name") |>
  pivot_longer(cols = starts_with("validation"), names_to = ("validation"), values_to = "val") |>
  filter(name == "Annotator1" & validation == "validation1" |
           name == "Annotator2" & validation == "validation2" |
           name == "Annotator3" & validation == "validation3" |
           name == "Annotator4" & validation == "validation4" |
           name == "Annotator5" & validation == "validation5")
glimpse(audit_r2_long)
```

```{r fit the glmer model}
samediff_all <- audit_r2_long |> 
  filter(val %in% c("Same Speaker","Different Speaker")) |>
  mutate(nVal = ifelse(val == "Same Speaker", 1, 0))
mod <- glmer(nVal ~ score + (1 | person) + (0 + score | person) + (1 | lang) + (0 + score | lang), family = "binomial", data = samediff_all)
summary(mod)
```

Get the threshold.

```{r obtain the threshold}
threshold <- -fixef(mod)[1]/fixef(mod)[2]
print(paste0("The threshold is ", round(threshold, 3)))
```

Plot the model result.

```{r plot the threshold}
# Adjust the figure plotting setting
#| fig-width: 6
#| fig-height: 3.5
#| fig-align: center


samediff_all$predicted <- predict(mod, type = "response", re.form = NA)
samediff_all$predicted_person <- predict(mod, type = "response")
preds <- ggpredict(mod, terms = "score[all]", interval = "confidence")

ggplot(samediff_all, aes(x = score, y = nVal)) +
  geom_jitter(alpha = 0.08, width = 0.05, height = 0.05) +
  # Confidence interval ribbon
  geom_ribbon(data = preds, aes(x = x, ymin = conf.low, ymax = conf.high), 
              fill = "deepskyblue3", alpha = 0.2, inherit.aes = FALSE) +
  # Model prediction line
  geom_line(data = preds, aes(x = x, y = predicted), 
            color = "deepskyblue3", size = 1.2, inherit.aes = FALSE) +
  scale_x_continuous(limits = c(-0.2, 1)) +
  labs(x = "Similarity score", y = "Probability") +
  geom_vline(xintercept = threshold, linetype = "dashed", color = "red") +
  theme(panel.grid.minor = element_blank(),
        axis.text.y = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        axis.title.x = element_text(size = 16)) 
#ggsave("~/Desktop/turning_point.pdf", plot=last_plot(), dpi = 300, height = 3, width = 7)

```


